---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Nghia Dai Tran"
date: "5/19/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This was built as part of a deliverable for the course Developing Data Products as part of the Coursera Data Science Specialization.

The app developed for the first part of the assignment demo is avalilable at: 
https://nghiasoft.shinyapps.io/c9w4/

Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/nghiasoft/c9w4

## Web Application functionality
- The sites is providing a tools for to help user know about
diamond price based on the quality of cut.  
- User can choose the quality of cut then they can see the Diamond Price
cistribution based on it.  
- The App also provide to user the summarize of the current data and detail data
frame of ech quality of cut.

## Dataset
The dataset containing the prices and other attributes of almost 54,000 diamonds.
A data frame with 53940 rows and 10 variables:  
- price: price in US dollars (\$326–\$18,823)  
- carat: weight of the diamond (0.2–5.01)  
- cut: quality of the cut (Fair, Good, Very Good, Premium, Ideal)  
- color: diamond colour, from J (worst) to D (best)  
- clarity: a measurement of how clear the diamond is (I1 (worst), SI1, SI2, VS1, VS2, VVS1, VVS2, IF (best))  
- x: length in mm (0–10.74)  
- y: width in mm (0–58.9)  
- z: depth in mm (0–31.8)  
- depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) (43–79)  
- table: width of top of diamond relative to widest point (43–95)

## The prices of diamonds based on its wight and quality of the cut

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(plotly)
set.seed(260689)
d <- diamonds[sample(nrow(diamonds), 1000), ]
p <- ggplot(data = d, aes(x = carat, y = price)) + ggtitle("") +
  geom_point(aes(text = paste("Clarity:", clarity))) +
  geom_smooth(aes(colour = cut, fill = cut)) + facet_wrap(~ cut)

ggplotly(p)
```

## Thank you
